---
title: "Covid-19/Return to Campus Survey"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)

covid <- read.csv(file = '/Users/laurenflemmer/Desktop/Projects/SVC/Data/covid:returntocampus.csv', header = TRUE, skip=2)

colorVector <- c("#B5CA8D", "#8BB174", "#426B69", "#222E50", "#2A4849", "#9A9B73")
colorVector2 <- c("#B5CA8D", "#8BB174", "#426B69", "#222E50", "#2A4849")

```


# Q7: How many of your Fall 2021 classes are on-campus?
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
colorVector1 <- c("#B5CA8D", "#8BB174", "#426B69", "#222E50", "#2A4849")

classesOnCampus <- covid %>% filter(X..ImportId...QID7.. != '') %>% select(X..ImportId...QID7..)
names(classesOnCampus)[1] <- "Response"

classesOnCampusPerc <- as.data.frame(table(classesOnCampus))
classesOnCampusPerc$Freq <- classesOnCampusPerc$Freq/sum(classesOnCampusPerc$Freq)
count.data1 <- classesOnCampusPerc %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(classesOnCampusPerc)[1] <- "Response"

```

```{r, echo=FALSE, warning=FALSE}
ggplot(data = classesOnCampusPerc, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector1, stat = "identity") + ggtitle("How many of your Fall 2021 classes are on-campus?") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 15, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')
```

# Q8: Do you believe UCR took adequate steps to return to campus (including hybrid/remote classes, vaccine requirements, test availability)
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
colorVector2 <- c("#B5CA8D", "#8BB174")

adequateSteps <- covid %>% filter(X..ImportId...QID8.. != '') %>% select(X..ImportId...QID8..)
names(adequateSteps)[1] <- "Response"

adequateSteps <- as.data.frame(table(adequateSteps))
adequateSteps$Freq <- adequateSteps$Freq/sum(adequateSteps$Freq)
count.data1 <- adequateSteps %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data1)[1] <- "Response"

```

```{r, echo=FALSE, warning=FALSE}
ggplot(count.data1, aes(x = "", y = Freq, fill = Response)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0)+
    geom_text(aes(label = paste(round(Freq / sum(Freq) * 100, 1), "%"), x = 1.2),
            position = position_stack(vjust = .5), color = "black", face = "bold", size = 4)+
  scale_fill_manual(values = colorVector2) +
  theme_void() +
  ggtitle(label = "Do you believe UCR took adequate steps to \n return to campus? (including hybrid/remote classes, \n vaccine requirements, test availability)*") +
          labs(caption = "*85.6% of responding students believe that UCR took adequate steps \n for the return to campus") + theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.25, vjust = -2.25, size = 16, face = "bold"), legend.title = element_text(size = 0), plot.caption = element_text(hjust = 0.05, vjust = 8, size = 10, face = "bold"), legend.text = element_text(size = 12))

```

#Q9: How comfortable do you feel regarding UCR’s decision to return to in-person? (1 being not comfortable at all, 5 being completely comfortable)
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

#OVERALL
allComfortable <- covid %>% filter(X..ImportId...QID9_1.. != "") %>% select(X..ImportId...QID9_1..)
allComfortable <- as.data.frame(table(allComfortable))
allComfortable$Freq <- allComfortable$Freq/sum(allComfortable$Freq)
count.data6 <- allComfortable %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data6)[1] <- "Response"

#CHASS
chassComfortable <- covid %>% filter(X..ImportId...QID3.. == "CHASS") %>% select(X..ImportId...QID9_1..)
chassComfortable <- as.data.frame(table(chassComfortable))
chassComfortable$Freq <- chassComfortable$Freq/sum(chassComfortable$Freq)
count.data2 <- chassComfortable %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(chassComfortable)[1] <- "Response"
#BCOE
bcoeComfortable <- covid %>% filter(X..ImportId...QID3.. == "BCOE") %>% select(X..ImportId...QID9_1..)
bcoeComfortable <- as.data.frame(table(bcoeComfortable))
bcoeComfortable$Freq <- bcoeComfortable$Freq/sum(bcoeComfortable$Freq)
count.data3 <- bcoeComfortable %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(bcoeComfortable)[1] <- "Response"
#CNAS
cnasComfortable <- covid %>% filter(X..ImportId...QID3.. == "CNAS") %>% select(X..ImportId...QID9_1..)
cnasComfortable <- as.data.frame(table(cnasComfortable))
cnasComfortable$Freq <- cnasComfortable$Freq/sum(cnasComfortable$Freq)
count.data4 <- cnasComfortable %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(cnasComfortable)[1] <- "Response"
#School of Business
sobComfortable <- covid %>% filter(X..ImportId...QID3.. == "School of Business") %>% select(X..ImportId...QID9_1..)
sobComfortable <- as.data.frame(table(sobComfortable))
sobComfortable$Freq <- sobComfortable$Freq/sum(sobComfortable$Freq)
count.data4 <- sobComfortable %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(sobComfortable)[1] <- "Response"
#School of Education
soeComfortable <- covid %>% filter(X..ImportId...QID3.. == "School of Education") %>% select(X..ImportId...QID9_1..)
soeComfortable <- as.data.frame(table(soeComfortable))
soeComfortable$Freq <- soeComfortable$Freq/sum(soeComfortable$Freq)
count.data4 <- soeComfortable %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(soeComfortable)[1] <- "Response"
#School of Public Policy
soppComfortable <- covid %>% filter(X..ImportId...QID3.. == "School of Public Policy") %>% select(X..ImportId...QID9_1..)
soppComfortable <- as.data.frame(table(soppComfortable))
soppComfortable$Freq <- soppComfortable$Freq/sum(soppComfortable$Freq)
count.data4 <- soppComfortable %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(soppComfortable)[1] <- "Response"


#first-year
firstYearComfortable <- covid %>% filter(X..ImportId...QID4.. == "1st") %>% select(X..ImportId...QID9_1..)
firstYearComfortable <- as.data.frame(table(firstYearComfortable))
firstYearComfortable$Freq <- firstYearComfortable$Freq/sum(firstYearComfortable$Freq)
count.data2 <- firstYearComfortable %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(firstYearComfortable)[1] <- "Response"
#second-year
secondYearComfortable <- covid %>% filter(X..ImportId...QID4.. == "2nd") %>% select(X..ImportId...QID9_1..)
secondYearComfortable <- as.data.frame(table(secondYearComfortable))
secondYearComfortable$Freq <- secondYearComfortable$Freq/sum(secondYearComfortable$Freq)
count.data2 <- secondYearComfortable %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(secondYearComfortable)[1] <- "Response"
#third-year
thirdYearComfortable <- covid %>% filter(X..ImportId...QID4.. == "3rd") %>% select(X..ImportId...QID9_1..)
thirdYearComfortable <- as.data.frame(table(thirdYearComfortable))
thirdYearComfortable$Freq <- thirdYearComfortable$Freq/sum(thirdYearComfortable$Freq)
count.data2 <- thirdYearComfortable %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(thirdYearComfortable)[1] <- "Response"
#fourth-year
fourthYearComfortable <- covid %>% filter(X..ImportId...QID4.. == "4th") %>% select(X..ImportId...QID9_1..)
fourthYearComfortable <- as.data.frame(table(fourthYearComfortable))
fourthYearComfortable$Freq <- fourthYearComfortable$Freq/sum(fourthYearComfortable$Freq)
count.data2 <- fourthYearComfortable %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(fourthYearComfortable)[1] <- "Response"
#fifth-year+
fifthYearComfortable <- covid %>% filter(X..ImportId...QID4.. == "5th (+)") %>% select(X..ImportId...QID9_1..)
fifthYearComfortable <- as.data.frame(table(fifthYearComfortable))
fifthYearComfortable$Freq <- fifthYearComfortable$Freq/sum(fifthYearComfortable$Freq)
count.data2 <- fifthYearComfortable %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(fifthYearComfortable)[1] <- "Response"
```

```{r, echo=FALSE, warning=FALSE}
colorVector1 <- c("#2A4849", "#2A4849","#426B69", "#222E50", "#8BB174")
colorVector <- c("#222E50", "#2A4849","#426B69", "#8BB174", "#B5CA8D")


#OVERALL
ggplot(data = count.data6, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector, stat = "identity") + ggtitle("How comfortable do you feel regarding UCR’s decision to \n return to in-person? (1 being not comfortable at all, 5 being \n completely comfortable) [ALL RESPONDING STUDENTS]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 15, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#CHASS
ggplot(data = chassComfortable, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector1, stat = "identity") + ggtitle("How comfortable do you feel regarding UCR’s decision to \n return to in-person? (1 being not comfortable at all, 5 being \n completely comfortable) [CHASS]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 15, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#BCOE
ggplot(data = bcoeComfortable, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector1, stat = "identity") + ggtitle("How comfortable do you feel regarding UCR’s decision to \n return to in-person? (1 being not comfortable at all, 5 being \n completely comfortable) [BCOE]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 15, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#CNAS
ggplot(data = cnasComfortable, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector1, stat = "identity") + ggtitle("How comfortable do you feel regarding UCR’s decision to \n return to in-person? (1 being not comfortable at all, 5 being \n completely comfortable) [CNAS]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 15, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#School of Business
ggplot(data = sobComfortable, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector1, stat = "identity") + ggtitle("How comfortable do you feel regarding UCR’s decision to \n return to in-person? (1 being not comfortable at all, 5 being \n completely comfortable) [School of Business]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 15, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#School of Education
ggplot(data = soeComfortable, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector1, stat = "identity") + ggtitle("How comfortable do you feel regarding UCR’s decision to \n return to in-person? (1 being not comfortable at all, 5 being \n completely comfortable) [School of Education]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 15, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#School of Public Policy
ggplot(data = soppComfortable, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector1, stat = "identity") + ggtitle("How comfortable do you feel regarding UCR’s decision to \n return to in-person? (1 being not comfortable at all, 5 being \n completely comfortable) [School of Public Policy]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 15, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')


#first-year
ggplot(data = firstYearComfortable, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector1, stat = "identity") + ggtitle("How comfortable do you feel regarding UCR’s decision to \n return to in-person? (1 being not comfortable at all, 5 being \n completely comfortable) [First-Year Students]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 15, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#second-year
ggplot(data = secondYearComfortable, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector1, stat = "identity") + ggtitle("How comfortable do you feel regarding UCR’s decision to \n return to in-person? (1 being not comfortable at all, 5 being \n completely comfortable) [Second-Year Students]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 15, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')
#third-year
ggplot(data = thirdYearComfortable, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector1, stat = "identity") + ggtitle("How comfortable do you feel regarding UCR’s decision to \n return to in-person? (1 being not comfortable at all, 5 being \n completely comfortable) [Third-Year Students]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 15, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')
#fourth-year
ggplot(data = fourthYearComfortable, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector1, stat = "identity") + ggtitle("How comfortable do you feel regarding UCR’s decision to \n return to in-person? (1 being not comfortable at all, 5 being \n completely comfortable) [Fourth-Year Students]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 15, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')
#fifth-year+
ggplot(data = fifthYearComfortable, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector1, stat = "identity") + ggtitle("How comfortable do you feel regarding UCR’s decision to \n return to in-person? (1 being not comfortable at all, 5 being \n completely comfortable) [Fifth-Year+ Students]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 15, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')
```

#Q11: What additional resources do you want available on campus? (Select all that apply)
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
covidNew <- covid
covid <- covid %>% 
    mutate(X..ImportId...QID12.. = strsplit(as.character(X..ImportId...QID12..), ",")) %>% 
    unnest(X..ImportId...QID12..)

resources <- covid %>% filter(X..ImportId...QID12.. != '') %>% select(X..ImportId...QID12..)
names(resources)[1] <- "Response"

resources <- as.data.frame(table(resources))
resources$Freq <- resources$Freq/sum(resources$Freq)
count.data1 <- resources %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data1)[1] <- "Response"

```

```{r, echo=FALSE, warning=FALSE}
colorVector3 <- c("#B5CA8D", "#8BB174", "#9A9B73", "#2A4849")
                 
ggplot(count.data1, aes(x = "", y = Freq, fill = Response)) +
  geom_bar(width = 1, stat = "identity", color = "dark grey") +
  coord_polar("y", start = 0)+
    geom_text(aes(label = paste(round(Freq / sum(Freq) * 100, 1), "%"), x = 1.2),
            position = position_stack(vjust = .5), color = "white", face = "bold", size = 4.5)+
  scale_fill_manual(values = colorVector3) +
  theme_void() +
  ggtitle(label = "What additional resources do you want available on campus? \n (Select all that apply)") +
           theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.25, vjust = -2.25, size = 17, face = "bold"), legend.title = element_text(size = 0), plot.caption = element_text(hjust = 0.05, vjust = 8, size = 10, face = "bold"), legend.text = element_text(size = 12))

```

#Q13: Has remote learning and/or Covid-19 restrictions negatively impacted your mental health (including feelings of sadness, depression, loneliness, stress, etc.)
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
colorVector1 <- c("#B5CA8D", "#8BB174", "#426B69", "#222E50", "#2A4849")
colorVector <- c("#222E50", "#2A4849","#426B69", "#8BB174", "#B5CA8D")

#overall
mental_overall <- covid %>% filter(X..ImportId...QID14.. != "") %>% select(X..ImportId...QID14..)
mental_overall <- as.data.frame(table(mental_overall))
mental_overall$Freq <- mental_overall$Freq/sum(mental_overall$Freq)
count.data.overallmental <- mental_overall %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.overallmental)[1] <- "Response"

#CHASS
chassNegativeImpact <- covid %>% filter(X..ImportId...QID3.. == "CHASS") %>% select(X..ImportId...QID14..)
chassNegativeImpact <- as.data.frame(table(chassNegativeImpact))
chassNegativeImpact$Freq <- chassNegativeImpact$Freq/sum(chassNegativeImpact$Freq)
count.data.Chass <- chassNegativeImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.Chass)[1] <- "Response"
#BCOE
bcoeNegativeImpact <- covid %>% filter(X..ImportId...QID3.. == "BCOE", X..ImportId...QID14.. != "") %>% select(X..ImportId...QID14..)
bcoeNegativeImpact <- as.data.frame(table(bcoeNegativeImpact))
bcoeNegativeImpact$Freq <- bcoeNegativeImpact$Freq/sum(bcoeNegativeImpact$Freq)
count.data.bcoe <- bcoeNegativeImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.bcoe)[1] <- "Response"
#CNAS
cnasNegativeImpact <- covid %>% filter(X..ImportId...QID3.. == "CNAS", X..ImportId...QID14.. != "") %>% select(X..ImportId...QID14..)
cnasNegativeImpact <- as.data.frame(table(cnasNegativeImpact))
cnasNegativeImpact$Freq <- cnasNegativeImpact$Freq/sum(cnasNegativeImpact$Freq)
count.data.cnas <- cnasNegativeImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.cnas)[1] <- "Response"
#School of Business
sobNegativeImpact <- covid %>% filter(X..ImportId...QID3.. == "School of Business", X..ImportId...QID14.. != "") %>% select(X..ImportId...QID14..)
sobNegativeImpact <- as.data.frame(table(sobNegativeImpact))
sobNegativeImpact$Freq <- sobNegativeImpact$Freq/sum(sobNegativeImpact$Freq)
count.data.sob <- sobNegativeImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.sob)[1] <- "Response"
#School of Education
soeNegativeImpact <- covid %>% filter(X..ImportId...QID3.. == "School of Education", X..ImportId...QID14.. != "") %>% select(X..ImportId...QID14..)
soeNegativeImpact <- as.data.frame(table(soeNegativeImpact))
soeNegativeImpact$Freq <- soeNegativeImpact$Freq/sum(soeNegativeImpact$Freq)
count.data.soe <- soeNegativeImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.soe)[1] <- "Response"
#School of Public Policy
soppNegativeImpact <- covid %>% filter(X..ImportId...QID3.. == "School of Public Policy", X..ImportId...QID14.. != "") %>% select(X..ImportId...QID14..)
soppNegativeImpact <- as.data.frame(table(soppNegativeImpact))
soppNegativeImpact$Freq <- soppNegativeImpact$Freq/sum(soppNegativeImpact$Freq)
count.data.sopp <- soppNegativeImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.sopp)[1] <- "Response"


#first-year
firstYearNegativeImpact <- covid %>% filter(X..ImportId...QID4.. == "1st", X..ImportId...QID14.. != "") %>% select(X..ImportId...QID14..)
firstYearNegativeImpact <- as.data.frame(table(firstYearNegativeImpact))
firstYearNegativeImpact$Freq <- firstYearNegativeImpact$Freq/sum(firstYearNegativeImpact$Freq)
count.data.first <- firstYearNegativeImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.first)[1] <- "Response"
#second-year
secondYearNegativeImpact <- covid %>% filter(X..ImportId...QID4.. == "2nd", X..ImportId...QID14.. != "") %>% select(X..ImportId...QID14..)
secondYearNegativeImpact <- as.data.frame(table(secondYearNegativeImpact))
secondYearNegativeImpact$Freq <- secondYearNegativeImpact$Freq/sum(secondYearNegativeImpact$Freq)
count.data.second <- secondYearNegativeImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.second)[1] <- "Response"
#third-year
thirdYearNegativeImpact <- covid %>% filter(X..ImportId...QID4.. == "3rd", X..ImportId...QID14.. != "") %>% select(X..ImportId...QID14..)
thirdYearNegativeImpact <- as.data.frame(table(thirdYearNegativeImpact))
thirdYearNegativeImpact$Freq <- thirdYearNegativeImpact$Freq/sum(thirdYearNegativeImpact$Freq)
count.data.third <- thirdYearNegativeImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.third)[1] <- "Response"
#fourth-year
fourthYearNegativeImpact <- covid %>% filter(X..ImportId...QID4.. == "4th", X..ImportId...QID14.. != "") %>% select(X..ImportId...QID14..)
fourthYearNegativeImpact <- as.data.frame(table(fourthYearNegativeImpact))
fourthYearNegativeImpact$Freq <- fourthYearNegativeImpact$Freq/sum(fourthYearNegativeImpact$Freq)
count.data.fourth <- fourthYearNegativeImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.fourth)[1] <- "Response"
#fifth-year+
fifthYearNegativeImpact <- covid %>% filter(X..ImportId...QID4.. == "5th (+)", X..ImportId...QID14.. != "") %>% select(X..ImportId...QID14..)
fifthYearNegativeImpact <- as.data.frame(table(fifthYearNegativeImpact))
fifthYearNegativeImpact$Freq <- fifthYearNegativeImpact$Freq/sum(fifthYearNegativeImpact$Freq)
count.data.fifth <- fifthYearNegativeImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.fifth)[1] <- "Response"
```

```{r, echo=FALSE, warning=FALSE}
colorVector5 <- c("#B5CA8D", "#8BB174")
colorVector6 <- c("#426B69", "#222E50")

#overall
ggplot(count.data.overallmental, aes(x = "", y = Freq, fill = Response)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0)+
    geom_text(aes(label = paste(round(Freq / sum(Freq) * 100, 1), "%"), x = 1.2),
            position = position_stack(vjust = .5), color = "black", face = "bold", size = 4)+
  scale_fill_manual(values = colorVector5) +
  theme_void() +
  ggtitle(label = "Has remote learning and/or Covid-19 restrictions negatively \n impacted your mental health (including feelings of \n sadness, depression, loneliness, stress, etc.) \n [ALL RESPONDING STUDENTS]*") +
          labs(caption = "*59.4% of responding UCR students believe that remote learning and/or \n Covid-19 restrictions have negatively imacted their mental health") + theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.25, vjust = -2.25, size = 16, face = "bold"), legend.title = element_text(size = 0), plot.caption = element_text(hjust = 0.05, vjust = 8, size = 10, face = "bold"), legend.text = element_text(size = 12))

#CHASS
ggplot(count.data.Chass, aes(x = "", y = Freq, fill = Response)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0)+
    geom_text(aes(label = paste(round(Freq / sum(Freq) * 100, 1), "%"), x = 1.2),
            position = position_stack(vjust = .5), color = "black", face = "bold", size = 4)+
  scale_fill_manual(values = colorVector5) +
  theme_void() +
  ggtitle(label = "Has remote learning and/or Covid-19 restrictions negatively \n impacted your mental health (including feelings of \n sadness, depression, loneliness, stress, etc.) [CHASS]*") +
          labs(caption = "*59.2% of responding CHASS students believe that remote learning and/or \n Covid-19 restrictions have negatively imacted their mental health") + theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.25, vjust = -2.25, size = 16, face = "bold"), legend.title = element_text(size = 0), plot.caption = element_text(hjust = 0.05, vjust = 8, size = 10, face = "bold"), legend.text = element_text(size = 12))

#BCOE
ggplot(count.data.bcoe, aes(x = "", y = Freq, fill = Response)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0)+
    geom_text(aes(label = paste(round(Freq / sum(Freq) * 100, 1), "%"), x = 1.2),
            position = position_stack(vjust = .5), color = "black", face = "bold", size = 4)+
  scale_fill_manual(values = colorVector5) +
  theme_void() +
  ggtitle(label = "Has remote learning and/or Covid-19 restrictions negatively \n impacted your mental health (including feelings of \n sadness, depression, loneliness, stress, etc.) [BCOE]*") +
          labs(caption = "*57.3% of responding BCOE students believe that remote learning and/or \n Covid-19 restrictions have negatively imacted their mental health") + theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.25, vjust = -2.25, size = 16, face = "bold"), legend.title = element_text(size = 0), plot.caption = element_text(hjust = 0.05, vjust = 8, size = 10, face = "bold"), legend.text = element_text(size = 12))

#CNAS
ggplot(count.data.cnas, aes(x = "", y = Freq, fill = Response)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0)+
    geom_text(aes(label = paste(round(Freq / sum(Freq) * 100, 1), "%"), x = 1.2),
            position = position_stack(vjust = .5), color = "black", face = "bold", size = 4)+
  scale_fill_manual(values = colorVector5) +
  theme_void() +
  ggtitle(label = "Has remote learning and/or Covid-19 restrictions negatively \n impacted your mental health (including feelings of \n sadness, depression, loneliness, stress, etc.) [CNAS]*") +
          labs(caption = "*64.7% of responding CNAS students believe that remote learning and/or \n Covid-19 restrictions have negatively imacted their mental health") + theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.25, vjust = -2.25, size = 16, face = "bold"), legend.title = element_text(size = 0), plot.caption = element_text(hjust = 0.05, vjust = 8, size = 10, face = "bold"), legend.text = element_text(size = 12))

#School of Business
ggplot(count.data.sob, aes(x = "", y = Freq, fill = Response)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0)+
    geom_text(aes(label = paste(round(Freq / sum(Freq) * 100, 1), "%"), x = 1.2),
            position = position_stack(vjust = .5), color = "black", face = "bold", size = 4)+
  scale_fill_manual(values = colorVector5) +
  theme_void() +
  ggtitle(label = "Has remote learning and/or Covid-19 restrictions negatively \n impacted your mental health (including feelings \n of sadness, depression, loneliness, stress, etc.) \n [School of Business]*") +
          labs(caption = "*49.8% of responding School of Business students believe that remote learning \n and/or Covid-19 restrictions have negatively imacted their mental health") + theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.25, vjust = -2.25, size = 16, face = "bold"), legend.title = element_text(size = 0), plot.caption = element_text(hjust = 0.05, vjust = 8, size = 10, face = "bold"), legend.text = element_text(size = 12))

#School of Education
ggplot(count.data.soe, aes(x = "", y = Freq, fill = Response)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0)+
    geom_text(aes(label = paste(round(Freq / sum(Freq) * 100, 1), "%"), x = 1.2),
            position = position_stack(vjust = .5), color = "black", face = "bold", size = 4)+
  scale_fill_manual(values = colorVector5) +
  theme_void() +
  ggtitle(label = "Has remote learning and/or Covid-19 restrictions negatively \n impacted your mental health (including feelings \n of sadness, depression, loneliness, stress, etc.) \n [School of Education]*") +
          labs(caption = "*44.2% of responding School of Education students believe that remote learning \n and/or Covid-19 restrictions have negatively imacted their mental health") + theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.25, vjust = -2.25, size = 16, face = "bold"), legend.title = element_text(size = 0), plot.caption = element_text(hjust = 0.05, vjust = 8, size = 10, face = "bold"), legend.text = element_text(size = 12))

#School of Public Policy
ggplot(count.data.sopp, aes(x = "", y = Freq, fill = Response)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0)+
    geom_text(aes(label = paste(round(Freq / sum(Freq) * 100, 1), "%"), x = 1.2),
            position = position_stack(vjust = .5), color = "black", face = "bold", size = 4)+
  scale_fill_manual(values = colorVector5) +
  theme_void() +
  ggtitle(label = "Has remote learning and/or Covid-19 restrictions negatively \n impacted your mental health (including feelings \n of sadness, depression, loneliness, stress, etc.) \n [School of Public Policy]*") +
          labs(caption = "*68.4% of responding School of Public Policy students believe that remote learning \n and/or Covid-19 restrictions have negatively imacted their mental health") + theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.25, vjust = -2.25, size = 16, face = "bold"), legend.title = element_text(size = 0), plot.caption = element_text(hjust = 0.05, vjust = 8, size = 10, face = "bold"), legend.text = element_text(size = 12))


#first-years
ggplot(count.data.first, aes(x = "", y = Freq, fill = Response)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0)+
    geom_text(aes(label = paste(round(Freq / sum(Freq) * 100, 1), "%"), x = 1.2),
            position = position_stack(vjust = .5), color = "white", face = "bold", size = 4)+
  scale_fill_manual(values = colorVector6) +
  theme_void() +
  ggtitle(label = "Has remote learning and/or Covid-19 restrictions negatively \n impacted your mental health (including feelings \n of sadness, depression, loneliness, stress, etc.) \n [First-Year Students]*") +
          labs(caption = "*51.1% of responding first-year students believe that remote learning \n and/or Covid-19 restrictions have negatively imacted their mental health") + theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.25, vjust = -2.25, size = 16, face = "bold"), legend.title = element_text(size = 0), plot.caption = element_text(hjust = 0.05, vjust = 8, size = 10, face = "bold"), legend.text = element_text(size = 12))

#second-years
ggplot(count.data.second, aes(x = "", y = Freq, fill = Response)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0)+
    geom_text(aes(label = paste(round(Freq / sum(Freq) * 100, 1), "%"), x = 1.2),
            position = position_stack(vjust = .5), color = "white", face = "bold", size = 4)+
  scale_fill_manual(values = colorVector6) +
  theme_void() +
  ggtitle(label = "Has remote learning and/or Covid-19 restrictions negatively \n impacted your mental health (including feelings \n of sadness, depression, loneliness, stress, etc.) \n [Second-Year Students]*") +
          labs(caption = "*63.1% of responding second-year students believe that remote learning \n and/or Covid-19 restrictions have negatively imacted their mental health") + theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.25, vjust = -2.25, size = 16, face = "bold"), legend.title = element_text(size = 0), plot.caption = element_text(hjust = 0.05, vjust = 8, size = 10, face = "bold"), legend.text = element_text(size = 12))

#third-years
ggplot(count.data.third, aes(x = "", y = Freq, fill = Response)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0)+
    geom_text(aes(label = paste(round(Freq / sum(Freq) * 100, 1), "%"), x = 1.2),
            position = position_stack(vjust = .5), color = "white", face = "bold", size = 4)+
  scale_fill_manual(values = colorVector6) +
  theme_void() +
  ggtitle(label = "Has remote learning and/or Covid-19 restrictions negatively \n impacted your mental health (including feelings \n of sadness, depression, loneliness, stress, etc.) \n [Third-Year Students]*") +
          labs(caption = "*63.3% of responding third-year students believe that remote learning \n and/or Covid-19 restrictions have negatively imacted their mental health") + theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.25, vjust = -2.25, size = 16, face = "bold"), legend.title = element_text(size = 0), plot.caption = element_text(hjust = 0.05, vjust = 8, size = 10, face = "bold"), legend.text = element_text(size = 12))

#fourth-years
ggplot(count.data.fourth, aes(x = "", y = Freq, fill = Response)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0)+
    geom_text(aes(label = paste(round(Freq / sum(Freq) * 100, 1), "%"), x = 1.2),
            position = position_stack(vjust = .5), color = "white", face = "bold", size = 4)+
  scale_fill_manual(values = colorVector6) +
  theme_void() +
  ggtitle(label = "Has remote learning and/or Covid-19 restrictions negatively \n impacted your mental health (including feelings \n of sadness, depression, loneliness, stress, etc.) \n [Fourth-Year Students]*") +
          labs(caption = "*66.1% of responding fourth-year students believe that remote learning \n and/or Covid-19 restrictions have negatively imacted their mental health") + theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.25, vjust = -2.25, size = 16, face = "bold"), legend.title = element_text(size = 0), plot.caption = element_text(hjust = 0.05, vjust = 8, size = 10, face = "bold"), legend.text = element_text(size = 12))

#fifth-years
ggplot(count.data.fifth, aes(x = "", y = Freq, fill = Response)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0)+
    geom_text(aes(label = paste(round(Freq / sum(Freq) * 100, 1), "%"), x = 1.2),
            position = position_stack(vjust = .5), color = "white", face = "bold", size = 4)+
  scale_fill_manual(values = colorVector6) +
  theme_void() +
  ggtitle(label = "Has remote learning and/or Covid-19 restrictions negatively \n impacted your mental health (including feelings \n of sadness, depression, loneliness, stress, etc.) \n [Fifth-Year+ Students]*") +
          labs(caption = "*60.6% of responding fifth-year+ students believe that remote learning \n and/or Covid-19 restrictions have negatively imacted their mental health") + theme(aspect.ratio = 1, plot.title = element_text(hjust = 0.25, vjust = -2.25, size = 16, face = "bold"), legend.title = element_text(size = 0), plot.caption = element_text(hjust = 0.05, vjust = 8, size = 10, face = "bold"), legend.text = element_text(size = 12))
```

#Q15: To what extent do you agree with the following statement: Covid-19 Restrictions (including online classes, remote learning, staying isolated) have impacted my education (including GPA, Major, higher education decisions, etc.).
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
colorVector6 <- c("#B5CA8D", "#8BB174", "#426B69", "#222E50")

#overall
overaallEduImpact <- covid %>% filter(X..ImportId...QID16.. != '') %>% select(X..ImportId...QID16..)
overaallEduImpact <- as.data.frame(table(overaallEduImpact))
overaallEduImpact$Freq <- overaallEduImpact$Freq/sum(overaallEduImpact$Freq)
count.data.overalledu <- overaallEduImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.overalledu)[1] <- "Response"
count.data.overalledu$Response <- factor(count.data.Chass$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#CHASS
chassEduImpact <- covid %>% filter(X..ImportId...QID3.. == "CHASS", X..ImportId...QID16.. != '') %>% select(X..ImportId...QID16..)
chassEduImpact <- as.data.frame(table(chassEduImpact))
chassEduImpact$Freq <- chassEduImpact$Freq/sum(chassEduImpact$Freq)
count.data.Chass <- chassEduImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.Chass)[1] <- "Response"
count.data.Chass$Response <- factor(count.data.Chass$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#BCOE
bcoeEduImpact <- covid %>% filter(X..ImportId...QID3.. == "BCOE", X..ImportId...QID16.. != '') %>% select(X..ImportId...QID16..)
bcoeEduImpact <- as.data.frame(table(bcoeEduImpact))
bcoeEduImpact$Freq <- bcoeEduImpact$Freq/sum(bcoeEduImpact$Freq)
count.data.bcoe <- bcoeEduImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.bcoe)[1] <- "Response"
count.data.bcoe$Response <- factor(count.data.bcoe$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#CNAS
cnasEduImpact <- covid %>% filter(X..ImportId...QID3.. == "CNAS", X..ImportId...QID16.. != "") %>% select(X..ImportId...QID16..)
cnasEduImpact <- as.data.frame(table(cnasEduImpact))
cnasEduImpact$Freq <- cnasEduImpact$Freq/sum(cnasEduImpact$Freq)
count.data.cnas <- cnasEduImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.cnas)[1] <- "Response"
count.data.cnas$Response <- factor(count.data.cnas$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#School of Business
sobEduImpact <- covid %>% filter(X..ImportId...QID3.. == "School of Business", X..ImportId...QID16.. != "") %>% select(X..ImportId...QID16..)
sobEduImpact <- as.data.frame(table(sobEduImpact))
sobEduImpact$Freq <- sobEduImpact$Freq/sum(sobEduImpact$Freq)
count.data.sob <- sobEduImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.sob)[1] <- "Response"
count.data.sob$Response <- factor(count.data.sob$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#School of Education
soeEduImpact <- covid %>% filter(X..ImportId...QID3.. == "School of Education", X..ImportId...QID16.. != "") %>% select(X..ImportId...QID16..)
soeEduImpact <- as.data.frame(table(soeEduImpact))
soeEduImpact$Freq <- soeEduImpact$Freq/sum(soeEduImpact$Freq)
count.data.soe <- soeEduImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.soe)[1] <- "Response"
count.data.soe$Response <- factor(count.data.soe$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#School of Public Policy
soppEduImpact <- covid %>% filter(X..ImportId...QID3.. == "School of Public Policy", X..ImportId...QID16.. != "") %>% select(X..ImportId...QID16..)
soppEduImpact <- as.data.frame(table(soppEduImpact))
soppEduImpact$Freq <- soppEduImpact$Freq/sum(soppEduImpact$Freq)
count.data.sopp <- soppEduImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.sopp)[1] <- "Response"
count.data.sopp$Response <- factor(count.data.sopp$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))


#first-year
firstYearEduImpact <- covid %>% filter(X..ImportId...QID4.. == "1st", X..ImportId...QID16.. != "") %>% select(X..ImportId...QID16..)
firstYearEduImpact <- as.data.frame(table(firstYearEduImpact))
firstYearEduImpact$Freq <- firstYearEduImpact$Freq/sum(firstYearEduImpact$Freq)
count.data.first <- firstYearEduImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.first)[1] <- "Response"
count.data.first$Response <- factor(count.data.first$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#second-year
secondYearEduImpact <- covid %>% filter(X..ImportId...QID4.. == "2nd", X..ImportId...QID16.. != "") %>% select(X..ImportId...QID16..)
secondYearEduImpact <- as.data.frame(table(secondYearEduImpact))
secondYearEduImpact$Freq <- secondYearEduImpact$Freq/sum(secondYearEduImpact$Freq)
count.data.second <- secondYearEduImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.second)[1] <- "Response"
count.data.second$Response <- factor(count.data.second$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#third-year
thirdYearEduImpact <- covid %>% filter(X..ImportId...QID4.. == "3rd", X..ImportId...QID16.. != "") %>% select(X..ImportId...QID16..)
thirdYearEduImpact <- as.data.frame(table(thirdYearEduImpact))
thirdYearEduImpact$Freq <- thirdYearEduImpact$Freq/sum(thirdYearEduImpact$Freq)
count.data.third <- thirdYearEduImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.third)[1] <- "Response"
count.data.third$Response <- factor(count.data.third$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#fourth-year
fourthYearEduImpact <- covid %>% filter(X..ImportId...QID4.. == "4th", X..ImportId...QID16.. != "") %>% select(X..ImportId...QID16..)
fourthYearEduImpact <- as.data.frame(table(fourthYearEduImpact))
fourthYearEduImpact$Freq <- fourthYearEduImpact$Freq/sum(fourthYearEduImpact$Freq)
count.data.fourth <- fourthYearEduImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.fourth)[1] <- "Response"
count.data.fourth$Response <- factor(count.data.fourth$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#fifth-year+
fifthYearEduImpact <- covid %>% filter(X..ImportId...QID4.. == "5th (+)", X..ImportId...QID16.. != "") %>% select(X..ImportId...QID16..)
fifthYearEduImpact <- as.data.frame(table(fifthYearEduImpact))
fifthYearEduImpact$Freq <- fifthYearEduImpact$Freq/sum(fifthYearEduImpact$Freq)
count.data.fifth <- fifthYearEduImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.fifth)[1] <- "Response"
count.data.fifth$Response <- factor(count.data.fifth$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))
```

```{r, echo=FALSE, warning=FALSE}

#overall
ggplot(data = count.data.overalledu, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my education (including GPA, Major, \n higher education decisions, etc.) [ALL RESPONDING STUDENTS]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 14, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#CHASS
ggplot(data = count.data.Chass, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my education (including GPA, Major, \n higher education decisions, etc.) [CHASS]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 14, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#BCOE
ggplot(data = count.data.bcoe, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my education (including GPA, Major, \n higher education decisions, etc.) [BCOE]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 14, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#CNAS
ggplot(data = count.data.cnas, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my education (including GPA, Major, \n higher education decisions, etc.) [CNAS]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 14, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#school of business
ggplot(data = count.data.sob, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my education (including GPA, Major, \n higher education decisions, etc.) [School of Business]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 14, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#School of Education
colorVector7 <- c("#B5CA8D", "#426B69", "#8BB174", "#222E50")
ggplot(data = count.data.soe, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector7, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my education (including GPA, Major, \n higher education decisions, etc.) [School of Education]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 14, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#School of Public Policy
colorVector8 <- c("#8BB174", "#B5CA8D", "#426B69", "#222E50")
ggplot(data = count.data.sopp, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector8, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my education (including GPA, Major, \n higher education decisions, etc.) [School of Public Policy]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 14, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#first-years
colorVector6 <- c("#B5CA8D", "#8BB174", "#426B69", "#222E50")
colorVector7 <- c("#B5CA8D", "#426B69", "#8BB174", "#222E50")
ggplot(data = count.data.first, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my education (including GPA, Major, \n higher education decisions, etc.) [First-Year Students]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 14, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#second-years
ggplot(data = count.data.second, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my education (including GPA, Major, \n higher education decisions, etc.) [Second-Year Students]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 14, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#third-years
ggplot(data = count.data.third, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my education (including GPA, Major, \n higher education decisions, etc.) [Third-Year Students]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 14, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#fourth-years
ggplot(data = count.data.fourth, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my education (including GPA, Major, \n higher education decisions, etc.) [Fourth-Year Students]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 14, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#fifth-years
ggplot(data = count.data.fifth, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my education (including GPA, Major, \n higher education decisions, etc.) [Fifth-Year+ Students]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 14, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')
```

#Q16: To what extent do you agree with the following statement: Covid-19 Restrictions (including online classes, remote learning, staying isolated) have impacted my future career plans (including career interest, job/internship availability, networking opportunities, etc.).
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
colorVector6 <- c("#B5CA8D", "#8BB174", "#426B69", "#222E50")
colorVector8 <- c("#B5CA8D", "#8BB174", "#426B69")
colorVector9 <- c("#426B69", "#B5CA8D", "#8BB174")

#overall
overallCarImpact <- covid %>% filter(X..ImportId...QID17.. != '') %>% select(X..ImportId...QID17..)
overallCarImpact <- as.data.frame(table(overallCarImpact))
overallCarImpact$Freq <- overallCarImpact$Freq/sum(overallCarImpact$Freq)
count.data.overall.car <- overallCarImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.overall.car)[1] <- "Response"
count.data.overall.car$Response <- factor(count.data.overall.car$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#CHASS
chassCarImpact <- covid %>% filter(X..ImportId...QID3.. == "CHASS", X..ImportId...QID17.. != '') %>% select(X..ImportId...QID17..)
chassCarImpact <- as.data.frame(table(chassCarImpact))
chassCarImpact$Freq <- chassCarImpact$Freq/sum(chassCarImpact$Freq)
count.data.Chass <- chassCarImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.Chass)[1] <- "Response"
count.data.Chass$Response <- factor(count.data.Chass$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#BCOE
bcoeCarImpact <- covid %>% filter(X..ImportId...QID3.. == "BCOE", X..ImportId...QID17.. != '') %>% select(X..ImportId...QID17..)
bcoeCarImpact <- as.data.frame(table(bcoeCarImpact))
bcoeCarImpact$Freq <- bcoeCarImpact$Freq/sum(bcoeCarImpact$Freq)
count.data.bcoe <- bcoeCarImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.bcoe)[1] <- "Response"
count.data.bcoe$Response <- factor(count.data.bcoe$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#CNAS
cnasCarImpact <- covid %>% filter(X..ImportId...QID3.. == "CNAS", X..ImportId...QID17.. != "") %>% select(X..ImportId...QID17..)
cnasCarImpact <- as.data.frame(table(cnasCarImpact))
cnasCarImpact$Freq <- cnasCarImpact$Freq/sum(cnasCarImpact$Freq)
count.data.cnas <- cnasCarImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.cnas)[1] <- "Response"
count.data.cnas$Response <- factor(count.data.cnas$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#School of Business
sobCarImpact <- covid %>% filter(X..ImportId...QID3.. == "School of Business", X..ImportId...QID17.. != "") %>% select(X..ImportId...QID17..)
sobCarImpact <- as.data.frame(table(sobCarImpact))
sobCarImpact$Freq <- sobCarImpact$Freq/sum(sobCarImpact$Freq)
count.data.sob <- sobCarImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.sob)[1] <- "Response"
count.data.sob$Response <- factor(count.data.sob$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#School of Education
soeCarImpact <- covid %>% filter(X..ImportId...QID3.. == "School of Education", X..ImportId...QID17.. != "") %>% select(X..ImportId...QID17..)
soeCarImpact <- as.data.frame(table(soeCarImpact))
soeCarImpact$Freq <- soeCarImpact$Freq/sum(soeCarImpact$Freq)
count.data.soe <- soeCarImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.soe)[1] <- "Response"
count.data.soe$Response <- factor(count.data.soe$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#School of Public Policy
soppCarImpact <- covid %>% filter(X..ImportId...QID3.. == "School of Public Policy", X..ImportId...QID17.. != "") %>% select(X..ImportId...QID17..)
soppCarImpact <- as.data.frame(table(soppCarImpact))
soppCarImpact$Freq <- soppCarImpact$Freq/sum(soppCarImpact$Freq)
count.data.sopp <- soppCarImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.sopp)[1] <- "Response"
count.data.sopp$Response <- factor(count.data.sopp$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))


#first-year
firstYearCarImpact <- covid %>% filter(X..ImportId...QID4.. == "1st", X..ImportId...QID17.. != "") %>% select(X..ImportId...QID17..)
firstYearCarImpact <- as.data.frame(table(firstYearCarImpact))
firstYearCarImpact$Freq <- firstYearCarImpact$Freq/sum(firstYearCarImpact$Freq)
count.data.first <- firstYearCarImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.first)[1] <- "Response"
count.data.first$Response <- factor(count.data.first$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#second-year
secondYearCarImpact <- covid %>% filter(X..ImportId...QID4.. == "2nd", X..ImportId...QID17.. != "") %>% select(X..ImportId...QID17..)
secondYearCarImpact <- as.data.frame(table(secondYearCarImpact))
secondYearCarImpact$Freq <- secondYearCarImpact$Freq/sum(secondYearCarImpact$Freq)
count.data.second <- secondYearCarImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.second)[1] <- "Response"
count.data.second$Response <- factor(count.data.second$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#third-year
thirdYearCarImpact <- covid %>% filter(X..ImportId...QID4.. == "3rd", X..ImportId...QID17.. != "") %>% select(X..ImportId...QID17..)
thirdYearCarImpact <- as.data.frame(table(thirdYearCarImpact))
thirdYearCarImpact$Freq <- thirdYearCarImpact$Freq/sum(thirdYearCarImpact$Freq)
count.data.third <- thirdYearCarImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.third)[1] <- "Response"
count.data.third$Response <- factor(count.data.third$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#fourth-year
fourthYearCarImpact <- covid %>% filter(X..ImportId...QID4.. == "4th", X..ImportId...QID17.. != "") %>% select(X..ImportId...QID17..)
fourthYearCarImpact <- as.data.frame(table(fourthYearCarImpact))
fourthYearCarImpact$Freq <- fourthYearCarImpact$Freq/sum(fourthYearCarImpact$Freq)
count.data.fourth <- fourthYearCarImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.fourth)[1] <- "Response"
count.data.fourth$Response <- factor(count.data.fourth$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))

#fifth-year+
fifthYearCarImpact <- covid %>% filter(X..ImportId...QID4.. == "5th (+)", X..ImportId...QID17.. != "") %>% select(X..ImportId...QID17..)
fifthYearCarImpact <- as.data.frame(table(fifthYearCarImpact))
fifthYearCarImpact$Freq <- fifthYearCarImpact$Freq/sum(fifthYearCarImpact$Freq)
count.data.fifth <- fifthYearCarImpact %>%
  arrange(desc(Freq)) %>%
  mutate(lab.ypos = cumsum(Freq) - 0.3*Freq)
names(count.data.fifth)[1] <- "Response"
count.data.fifth$Response <- factor(count.data.fifth$Response, levels = c("Unsure", "Not at all", "Somewhat", "A lot"))
```

```{r, echo=FALSE, warning=FALSE}

#overall
ggplot(data = count.data.overall.car, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my future career plans (including career interest, \n job/internship availability, networking opportunities, etc.) \n [ALL RESPONDING STUDENTS]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 14, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#CHASS
ggplot(data = count.data.Chass, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my future career plans (including career interest, \n job/internship availability, networking opportunities, etc.) [CHASS]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 14, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#BCOE
ggplot(data = count.data.bcoe, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my future career plans (including career interest, \n job/internship availability, networking opportunities, etc.) [BCOE]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 14, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#CNAS
ggplot(data = count.data.cnas, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my future career plans (including career interest, \n job/internship availability, networking opportunities, etc.) [CNAS]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 14, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#school of business
ggplot(data = count.data.sob, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) have \n impacted my future career plans (including career interest, job/internship \n availability, networking opportunities, etc.) [School of Business]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 13, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#School of Education
colorVector7 <- c("#B5CA8D", "#426B69", "#8BB174", "#222E50")
ggplot(data = count.data.soe, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector9, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) have \n impacted my future career plans (including career interest, job/internship \n availability, networking opportunities, etc.) [School of Education]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 13, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold') + geom_text(aes(x='Unsure', y = 0), label = "0%") + scale_x_discrete(drop=FALSE)

#School of Public Policy
colorVector9 <- c("#B5CA8D", "#8BB174", "#426B69")
ggplot(data = count.data.sopp, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector9, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) have \n impacted my future career plans (including career interest, job/internship \n availability, networking opportunities, etc.) [School of Public Policy]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 13, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold') + geom_text(aes(x='Unsure', y = 0), label = "0%") + scale_x_discrete(drop=FALSE)

#first-years
colorVector6 <- c("#B5CA8D", "#8BB174", "#426B69", "#222E50")
colorVector7 <- c("#B5CA8D", "#426B69", "#8BB174", "#222E50")
ggplot(data = count.data.first, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector7, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my future career plans (including career interest, job/internship \n availability, networking opportunities, etc.) [First-Year Students]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 13, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#second-years
ggplot(data = count.data.second, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my future career plans (including career interest, job/internship \n availability, networking opportunities, etc.) [Second-Year Students]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 13, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#third-years
ggplot(data = count.data.third, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my future career plans (including career interest, job/internship \n availability, networking opportunities, etc.) [Third-Year Students]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 13, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#fourth-years
ggplot(data = count.data.fourth, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my future career plans (including career interest, job/internship \n availability, networking opportunities, etc.) [Fourth-Year Students]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 13, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')

#fifth-years
ggplot(data = count.data.fifth, mapping = aes(x = Response, y = Freq)) +
  geom_bar(fill = colorVector6, stat = "identity") + ggtitle("To what extent do you agree with the following statement: Covid-19 \n Restrictions (including online classes, remote learning, staying isolated) \n have impacted my future career plans (including career interest, job/internship \n availability, networking opportunities, etc.) [Fifth-Year+ Students]") +
  xlab("Response") +
  ylab("Count") +
  theme(axis.text.x=element_text(color = "black", size=11, vjust = 0.8), axis.text.y=element_text(color = "black", size=10, vjust = 0.8), plot.title = element_text(hjust = 0.3, size = 13, face = "bold"), legend.title = element_text(size = 8, face = "bold"), axis.title.x = element_text(size = 11, face = "bold"), axis.title.y = element_text(size = 11, face = "bold"), plot.subtitle = element_text(size = 11, hjust = 0.3), legend.key.size = unit(0.4, 'cm'), legend.key.height = unit(0.4, 'cm'), legend.key.width = unit(0.4, 'cm'), legend.text = element_text(size=7)) +
geom_text(aes(x = Response, y = Freq + 0.015, label = paste(round(Freq, 3)*100, '%')), size = 4, color = 'black', face = 'bold')
```
